---
title: "Exploratory Analysis of College Major and Income Data"
author: "Gaurav Sharma"
date: "10/07/2020"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	fig.height = 5,
	fig.width = 8,
	cache = TRUE,
	dpi = 180
)
library(tidyverse)
library(scales)
library(ggrepel)
library(broom)
library(plotly)
theme_set(theme_light())
```

```{r}
tt_file <- tidytuesdayR::tt_load("2018-10-16")
recent_grads <- tt_file$`recent-grads`

major_processed  <- recent_grads %>% 
    arrange(desc(Median)) %>% 
    mutate(Major = str_to_title(Major),
           Major = fct_reorder(Major, Median))
```

### What is the median salary for major graduates in the country
```{r}
recent_grads %>% 
    ggplot(aes(Median)) +
    geom_histogram()
```

### What categories of major make more money 
```{r}
recent_grads %>% 
    mutate(Major_category = fct_reorder(Major_category, Median)) %>% 
    ggplot(aes(Median, Major_category)) +
    geom_boxplot() +
    scale_x_continuous(labels = dollar_format())
```

### What categories of major make more money (Median Salary)
```{r}
recent_grads %>% 
    group_by(Major_category) %>% 
    summarise(Median = median(Median)) %>% 
    mutate(Major_category = fct_reorder(Major_category, Median)) %>% 
    ggplot(aes(Median, Major_category)) +
    geom_col() +
    scale_x_continuous(labels = dollar_format())
```

### Which are the highest earning majors
```{r}
recent_grads %>% 
    arrange(desc(Median)) %>% 
    select(Major, Major_category, Median, P25th, P75th, Sample_size) %>%
    filter(Sample_size >= 100) %>% 
    head(20) %>% 
    mutate(Major = str_to_title(Major),
           Major = fct_reorder(Major, Median)) %>% 
    ggplot(aes(Major, Median, color = Major_category)) +
    geom_point() +
    geom_errorbar(aes(ymin = P25th, ymax = P75th)) +
    coord_flip() +
    scale_y_continuous(labels = dollar_format()) +
    expand_limits(y = 0) +
    labs(title = "Which are the highest earning majors",
         subtitle = "Chosen from the majors where atleast 100 graduates were surveyed. Bars represent IQR",
         x = "",
         y = "Median Salary of Graduates")
    
```

### Which are the lowest earning majors

```{r}
recent_grads %>% 
    arrange(desc(Median)) %>% 
    select(Major, Major_category, Median, P25th, P75th, Sample_size) %>%
    filter(Sample_size >= 100) %>% 
    tail(20) %>% 
    mutate(Major = str_to_title(Major),
           Major = fct_reorder(Major, Median)) %>% 
    ggplot(aes(Major, Median, color = Major_category)) +
    geom_point() +
    geom_errorbar(aes(ymin = P25th, ymax = P75th)) +
    coord_flip() +
    scale_y_continuous(labels = dollar_format()) +
    expand_limits(y = 0) +
    labs(title = "Which are the lowest earning majors",
         subtitle = "Top 20 Majors chosen from the majors where atleast 100 graduates were surveyed. Bars represent IQR",
         x = "",
         y = "Median Salary of Graduates")

```

### Lets see if we are seeing some of the majors having high median salaries just because the sample size was too small for them. Lets' confirm it.
```{r}
recent_grads %>% 
    arrange(desc(Median)) %>% 
    select(Major, Major_category, Median, P25th, P75th, Sample_size) %>% 
    mutate(Major = str_to_title(Major),
           Major = fct_reorder(Major, Median)) %>% 
    ggplot(aes(Sample_size, Median)) +
    geom_point() +
    geom_text(aes(label = Major), check_overlap = T, vjust = 1, hjust = 1) +
    scale_x_log10()
    
```

### What are the most common majors
```{r}
recent_grads %>% 
    arrange(desc(Total)) %>% 
    head(20) %>%
    select(Major, Major_category, Total) %>% 
    mutate(Major = str_to_title(Major),
           Major = fct_reorder(Major, Total)) %>% 
    ggplot(aes(Major, Total, fill = Major_category, color = Major_category)) +
    geom_col() +
    coord_flip() +
    scale_y_continuous(labels = comma_format()) 
```

### What are the most common major categories
```{r}
recent_grads %>% 
    count(Major_category,wt = Total, sort = T) %>% 
    mutate(Major_category = str_to_title(Major_category),
           Major_category = fct_reorder(Major_category, n)) %>% 
    ggplot(aes(Major_category, n, fill = Major_category)) +
    geom_col() +
    coord_flip() +
    theme(legend.position = "none") +
    scale_y_continuous(labels = comma_format())

```

### How gender relates to major categories
```{r}
recent_grads %>% 
    pivot_longer(Men:Women, names_to = "Gender", values_to = "Number") %>% 
    select(Major_category, Gender, Number) %>% 
    count(Major_category, Gender, wt = Number, sort = T) %>% 
    mutate(Major_category = fct_reorder(Major_category, n)) %>% 
    ggplot(aes(Major_category, n, color = Gender, fill = Gender)) +
    geom_col() +
    coord_flip() +
    scale_y_continuous(labels = comma_format()) +
    labs(x ="",
         y = "Number of Graduates")
    
    
```

### How gender relates to major studies
```{r}

recent_grads %>% 
    arrange(desc(Median)) %>% 
    mutate(Major = str_to_title(Major),
           Major = fct_reorder(Major, Median)) %>% 
    arrange(desc(Total)) %>% 
    head(20) %>% 
    pivot_longer(Men:Women, names_to = "Gender", values_to = "Number") %>%
    select(Major, Gender, Number) %>%
    mutate(Major = fct_reorder(Major, Number)) %>% 
    ggplot(aes(Major, Number, color = Gender, fill = Gender)) +
    geom_col(alpha = 0.7) +
    coord_flip() +
    scale_y_continuous(labels = comma_format()) +
    labs(x ="",
         y = "Number of Graduates")

```

### Share of women is higher in majors such as Psychology, Health and Business
```{r}
recent_grads %>% 
    select(Major, Major_category, ShareWomen, Total) %>% 
    drop_na() %>% 
    mutate(Major = str_to_title(Major)) %>% 
    ggplot(aes(Total, ShareWomen)) +
    geom_point(aes(color = Major), size = 2) +
    geom_text(aes(label = Major, color = Major), check_overlap = T, hjust =1, vjust = 1) +
    theme(legend.position = "none") +
    scale_x_continuous(labels = comma_format()) +
    coord_flip()

```

```{r by major category}
by_major_category <- recent_grads %>% 
    filter(!is.na(Total)) %>% 
    group_by(Major_category) %>% 
    summarise(Men = sum(Men),
              Women = sum(Women),
              Total = sum(Total),
              Median_Salary = sum(Median*Sample_size)/sum(Sample_size)) %>% 
    ungroup() %>% 
    mutate(ShareWomen = Women/Total) %>% 
    arrange(desc(ShareWomen))
```

```{r}

by_major_category %>% 
    ggplot(aes(ShareWomen, Median_Salary)) +
    geom_point() +
    geom_smooth(method = "lm") +
    geom_text_repel(aes(label = Major_category), hjust = 1, vjust = 1) +
    expand_limits(y = 0)
```

```{r}
g <- major_processed %>% 
    ggplot(aes(ShareWomen, Median)) +
    geom_point(aes(color = Major_category, size = Sample_size, label = Major), alpha = 0.8) +
    geom_smooth(method = "lm") +
    expand_limits(y = 0) +
    scale_x_continuous(labels = percent_format()) +
    theme(legend.position = "none")
g
```

```{r}
#ggplotly(g)

```

```{r}
major_lm <- major_processed %>% 
    select(Major,Total, ShareWomen,Sample_size, Median) %>% 
    lm(Median ~ ShareWomen, data = ., weights = Sample_size) %>% 
    summary()
major_lm
```

```{r}
major_lm_grouped <- major_processed %>% 
    select(Major,Major_category, Total, ShareWomen, Sample_size, Median) %>% 
    add_count(Major_category) %>% 
    filter(n>=10) %>% 
    nest(-Major_category) %>% 
    mutate(model = map(data, ~lm(Median~ShareWomen, weights = Sample_size, data = .)),
           tidied = map(model, tidy)) %>% 
    unnest(tidied) %>% 
    filter(term == "ShareWomen") %>% 
    arrange(estimate) %>% 
    mutate(fdr = p.adjust(p.value, method = "fdr"))
major_lm_grouped
```

### End of Report





